Plot curve fits

### 2023-01-17 Working Rmds/plot_fits.Rmd
Plot fits both natural and log scale, both concentration/dose and dose-faceted concentrations.

```{r}
timestamp <- "2023_01_11"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
timestamp,
".csv"))
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

@@

Keep parameters only.

@@

Merge the parameter information with the original concentration-time info.

@@

  #Melt to longer format. The effect will be as though we row-bound two versions
  #of DF together: one with the original single references, and one with
  #comma-separated combined References. There is one column "Study_type" that
  #contains either "Study" or "Study_pooled", and then one column "Study" that
  #contains the studyID or the comma-separated list of study IDs.
  cvt1 <- melt(cvt,
              measure.vars = c("Study", "Study_pooled"),
              variable.name = "Study_type",
              value.name = "Study")

  #There will be duplicated rows for single-study analyses, because
  #"Study_pooled" (the comma-separated list of study IDs) is the same as "Study"
  #(the individual study ID) for these analyses. Remove the duplicated rows.
  cvt1 <- unique(cvt1[, .(DTXSID, Compound, Species, Study,Reference,
                        Route, Dose, iv, Media, Time, Value, LOQ, Value_SD, N_Subjects)])

  cvt_fit <- pk_params[cvt1, 
                    on = c("DTXSID" = "DTXSID",
                            "Species" = "Species",
                            "Studies.Analyzed" = "Study"),
                     allow.cartesian = TRUE]
```

@@

Get unique combinations of DTXSID and species -- each of these will be one plot.

```{r}
plot_table <- unique(pk_fit[, .(DTXSID, Species)])
```

Plot all models for the joint analysis.
```{r}
cvt_fit[,
        plot_fit(DTXSID = unique(DTXSID),
                 Species_in = unique(Species),
                 DFsub = .SD,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly",
                 verbose = TRUE),
        by = .(DTXSID,
               Species),
        .SDcols = names(cvt_fit)]

>>>>

```{r}
timestamp <- "2023_01_13"
```

@@

```{r, load_cvt, eval = TRUE}
cvt <- fread(paste0("../inst/ext/cvt_preprocessed_",
"2023_01_13",
".csv"))
cvt[, Reference:=as.character(Reference)]
cvt[, Reference_orig:=as.character(Reference_orig)]
```

@@

Keep parameters only -- that is, drop the calculated quantities like tpeak, Cpeak, Css, total clearance, etc.

@@

Merge the parameter information with the original concentration-time data.

@@

  #Melt to longer format. The effect will be as though we row-bound two versions
  #of DF together: one with the original single references, and one with
  #comma-separated combined References. There is one column "Study_type" that
  #contains either "Study" or "Study_pooled", and then one column "Study" that
  #contains the studyID or the comma-separated list of study IDs.
cvt[, Study_orig := Study]
  cvt1 <- melt(cvt,
              measure.vars = c("Study", "Study_pooled"),
              variable.name = "Study_type",
              value.name = "Studies.Analyzed")

  #There will be duplicated rows for single-study analyses, because
  #"Study_pooled" (the comma-separated list of study IDs) is the same as "Study"
  #(the individual study ID) for these analyses. Remove the duplicated rows.
  cvt1 <- unique(cvt1[, .(DTXSID, Compound, Species, Studies.Analyzed, Reference,
                        Route, Dose, iv, Media, Study_orig, Time,
                        Value, LOQ, Value_SD, N_Subjects,
                        Conc, Conc_Dose, Detect, Value_Dose,
                        Value_SD_Dose, LOQ_Dose)])

  cvt_fit <- pk_params[cvt1, 
                    on = c("DTXSID" = "DTXSID",
                            "Species" = "Species",
                            "Studies.Analyzed" = "Studies.Analyzed"),
                     allow.cartesian = TRUE]
```

Also prepare a table of study-specific sigmas.

```{r}
DT_1comp <- fread(paste0("../inst/ext/", "PK_fit_table_1comp_", timestamp, ".csv",sep=""))
DT_2comp <- fread(paste0("../inst/ext/", "PK_fit_table_2comp_", timestamp, ".csv",sep=""))
DT_flat <- fread(paste0("../inst/ext/", "PK_fit_table_flat_", timestamp, ".csv",sep=""))

idcols <- c( "Analysis_Type",
                                 "DTXSID",
                                "Species",
                                "References.Analyzed",
                               "Studies.Analyzed")

DT_all <- rbindlist(list(DT_1comp, DT_2comp, DT_flat),
                    use.names = TRUE,
                    fill = TRUE)
  DT_all <- DT_all[grepl(x = param_name,
                 pattern = "sigma"),
           .SD, .SDcols= c(idcols, "model", "param_name", "Fitted mean", "Fitted std dev")]
  DT_melt <- dcast(DT_all,
                   formula = Analysis_Type + DTXSID + Species + References.Analyzed + Studies.Analyzed + param_name ~ model,
                   value.var = "Fitted mean")
  setnames(DT_melt,
           unique(DT_all$model),
           paste0("sigma.", unique(DT_all$model)))
  DT_melt[param_name %in% "sigma", sigma_studyID := Studies.Analyzed]
  DT_melt[!(param_name %in% "sigma"), sigma_studyID := gsub(x = param_name,
                                                            pattern = "sigma_study_",
                                                            replacement = "",
                                                            fixed = TRUE)]
  DT_melt_sd <- dcast(DT_all,
                   formula = Analysis_Type + DTXSID + Species + References.Analyzed + Studies.Analyzed + param_name ~ model,
                   value.var = "Fitted std dev")
   setnames(DT_melt_sd,
           unique(DT_all$model),
           paste0("sigma_sd.", unique(DT_all$model)))
 DT_melt_sd[param_name %in% "sigma", sigma_studyID := Studies.Analyzed]
  DT_melt_sd[!(param_name %in% "sigma"), sigma_studyID := gsub(x = param_name,
                                                            pattern = "sigma_study_",
                                                            replacement = "",
                                                            fixed = TRUE)]

  DT_melt_all <- merge(DT_melt, DT_melt_sd, by = intersect(names(DT_melt),
                                                           names(DT_melt_sd)))

Get SD of data for each study

```{r}
cvt_sd <- cvt_fit[, .(sd_Value_Dose = sd(Value_Dose, na.rm = TRUE)),
        by = Study_orig]
```

Merge SD of data with fitted SDs and compare

```{r}
sd_table <- cvt_sd[DT_melt_all,
      on = c("Study_orig" = "sigma_studyID")]
```

@@

Plot all models for the joint analysis.
```{r}
cvt_fit[,
        plot_fit(DTXSID = unique(DTXSID),
                 Species_in = unique(Species),
                 DFsub = .SD,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 plot_dose_norm = TRUE,
                 split_dose = FALSE,
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                 file_suffix = "errbars_naturaly_dose_norm",
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_norm",
                 verbose = TRUE),
        by = .(DTXSID,
               Species),
        .SDcols = names(cvt_fit)]

```
Do the same, but faceting by dose.

```{r}
cvt_fit[,
        plot_fit(DTXSID = unique(DTXSID),
                 Species_in = unique(Species),
                 DFsub = .SD,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 plot_dose_norm = FALSE,
                 split_dose = TRUE,
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = FALSE,
                     plot_errbars = TRUE,
                     log10_scale_time = FALSE,
                 file_suffix = "errbars_naturaly_dose_norm",
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/errbars_naturaly/dose_split",
                 verbose = TRUE),
        by = .(DTXSID,
               Species),
        .SDcols = names(cvt_fit)]

Do non-dose-faceted, but log scale.

```{r}
cvt_fit[,
        plot_fit(DTXSID = unique(DTXSID),
                 Species_in = unique(Species),
                 DFsub = .SD,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 plot_dose_norm = TRUE,
                 split_dose = FALSE,
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = TRUE,
                     plot_errbars = FALSE,
                     log10_scale_time = FALSE,
                 file_suffix = "errbars_naturaly_dose_norm",
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_norm",
                 verbose = TRUE),
        by = .(DTXSID,
               Species),
        .SDcols = names(cvt_fit)]

Do dose-faceted, but log scale.

```{r}
cvt_fit[,
        plot_fit(DTXSID = unique(DTXSID),
                 Species_in = unique(Species),
                 DFsub = .SD,
                 model_in = "all",
                 Analysis_Type_in = "Joint",
                 plot_dose_norm = FALSE,
                 split_dose = TRUE,
                 n_interp_time = 10,
                     limit_y_axis = FALSE,
                     log10_scale_y = TRUE,
                     plot_errbars = FALSE,
                     log10_scale_time = FALSE,
                 file_suffix = "errbars_naturaly_dose_norm",
                     file_path = "../inst/ext/plots/Joint Analysis/model_all/noerrbars_logy/dose_split",
                 verbose = TRUE),
        by = .(DTXSID,
               Species),
        .SDcols = names(cvt_fit)]
